### 2020-04-04 system-model.tex
:pencil: Composite channel

    \begin{section} {System Model}
        Consider an IRS-aided multiuser MISO SWIPT system where the IRS not only assists the primal transmission but also retrieves channel state information (CSI) and harvests energy for its own operation. The $M$-antenna transmitter delivers information and power simultaneously, through the $U$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands. It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}. Due to the passive characteristics of IRS, we consider a time-division duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity. Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system. The signals reflected by IRS for two and more times are assumed negligible and thus not considered. The channel is assumed to be unchanged within each transmission frame and the quasi-static frequency-selective model is used for both the user-AP and user-IRS-AP links. A superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, are designed adaptively to maximize the rate-energy tradeoff \cite{Clerckx2018b}. Note that although frequency selective surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus prohibitive while passive FSS is not reconfigurable with fixed physical characteristics \cite{Kim2006,Xu2014,Anwar2018}. Therefore, we assume a frequency-flat IRS with same reflection coefficients for all subbands.

@@

        \begin{subsection} {Composite Channel Model}
            Consider a single-IRS scenario in a multipath environment. The frequency response of the AP-user (i.e. direct) channel between antenna $m$ and user $k$ at subband $n$ is $h_{D,n,m,k}=A_{D,n,m,k}e^{j\bar{\psi}_{D,n,m,k}}=\sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} e^{j\left( -2 \pi f_n \tau_{l_{D,k}}+\varsigma_{l_{D,k},n,m,k} \right)}$, where $L_{D,k}$ is the number of paths in the direct link of user $k$, $\alpha_{l_{D,k}}$ and $\tau_{l_{D,k}}$ are the delay and amplitude gain of the $l_{D,k}$-th path, $\varsigma_{l_{D,k},n,m,k}$ is the phase shift of the $l_{D,k}$-path between transmit antenna $m$ and the receive antenna of user $k$ at subband $n$. Similarly, the AP-IRS (i.e. incident) channel between antenna $m$ and element $u$ at subband $n$ writes as $h_{I,n,m,u}=A_{I,n,m,u}e^{j\bar{\psi}_{I,n,m,u}}=\sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e. reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k}=A_{R,n,u,k}e^{j\bar{\psi}_{R,n,u,k}}=\sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$. Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.

            Stack the entries and denote the baseband equivalent channel from the AP to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, from the AP to the IRS as $\boldsymbol{h}_I \in \mathbb{C}^{U \times MN}$, and from the IRS to user $k$ as $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$. Element $u$ of the IRS receives a superposed waveform transmitted by $M$ antennas after the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$ where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift. Note each passive reflector need to absorb a small portion ($1 - \beta_u$) of the signal, then combine and harvest it to support information decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$. With the assumption of frequency-flat IRS, the IRS reflecting coefficient matrix $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$ is obtained by stacking $R_0$ over $N$ subbands. The IRS-aided extra link from the AP to user $k$ can be modeled as a concatenation of the AP-IRS channel, the IRS reflection, and the IRS-user channel. Both the direct link and the IRS-aided link contributes to the overall channel of user $k$ and the composite channel for user $k$ writes as
            \begin{equation} \label{eq:h_k}
                \boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{\boldsymbol{h}_I} \right)
            \end{equation}
        \end{subsection}

        \begin{subsection} {Received Signal}
            In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links. It can be expressed as
            \begin{equation} \label{eq:y_{m,k}(t)}
                \begin{split}
                    y_{m,k}(t)
                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\} \\
                    &\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
                    &= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}
                \end{split}
            \end{equation}
            Therefore, the RF signal input to the antenna at user $k$ is
            \begin{equation} \label{eq:y_{k}(t)}
                y_{k}(t) = \sum_{m=1}^{M} y_{m,k}(t)
            \end{equation}
        \end{subsection}
    \end{section}

>>>>

\begin{section} {System Model}
	Consider an IRS-aided multiuser MISO SWIPT system where the IRS not only assists the primal transmission but also retrieves channel state information (CSI) and harvests energy for its own operation. The $M$-antenna transmitter delivers information and power simultaneously, through the $U$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands. It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}. Due to the passive characteristics of IRS, we consider a time-division duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity. Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system. The signals reflected by IRS for two and more times are assumed negligible and thus not considered. The channel is assumed to be unchanged within each transmission frame and the quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links. A superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, are designed adaptively to maximize the rate-energy tradeoff \cite{Clerckx2018b}. Note that although frequency selective surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive while passive FSS is not reconfigurable with fixed physical characteristics \cite{Kim2006,Xu2014,Anwar2018}. Therefore, we assume a frequency-flat IRS with same reflection coefficients for all subbands.

@@

	\begin{subsection} {Composite Channel Model}
		% Consider a single-IRS scenario in a multipath environment. The frequency response of the AP-user (i.e. direct) channel between antenna $m$ and user $k$ at subband $n$ is $h_{D,n,m,k}=A_{D,n,m,k}e^{j\bar{\psi}_{D,n,m,k}}=\sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} e^{j\left( -2 \pi f_n \tau_{l_{D,k}}+\varsigma_{l_{D,k},n,m,k} \right)}$, where $L_{D,k}$ is the number of paths in the direct link of user $k$, $\alpha_{l_{D,k}}$ and $\tau_{l_{D,k}}$ are the delay and amplitude gain of the $l_{D,k}$-th path, $\varsigma_{l_{D,k},n,m,k}$ is the phase shift of the $l_{D,k}$-path between transmit antenna $m$ and the receive antenna of user $k$ at subband $n$. Similarly, the AP-IRS (i.e. incident) channel between antenna $m$ and element $u$ at subband $n$ writes as $h_{I,n,m,u}=A_{I,n,m,u}e^{j\bar{\psi}_{I,n,m,u}}=\sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e. reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k}=A_{R,n,u,k}e^{j\bar{\psi}_{R,n,u,k}}=\sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$. Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.;

		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{U \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$ respectively. At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $U$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times U}$. Similarly, the $n$-th incident channel gain matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$. Element $u$ of the IRS receives a superposed waveform after the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively. Each passive reflector harvests a small portion ($1 - \beta_u$) of the signal to support CSI decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$. With the assumption of frequency-flat reflection, the IRS matrix is obtained by stacking $\boldsymbol{R}_0$ over $N$ subbands such that $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$. The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel. Both the direct link and the IRS-aided link contributes to the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times MN}$ as
		\begin{equation} \label{eq:h_k}
			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{\boldsymbol{H}_I} \right)
		\end{equation}
		On top of this, we select the $n$-th of every $N$ entries and combine them to form the subchannel as $\boldsymbol{h}_{k,n}=[h_{k,n,m},\dots,h_{k,n,M}] \in \mathbb{C}^{1 \times M}$ to describe the frequency response at subband $n$ for user $k$, with $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}$.
	\end{subsection}

	\begin{subsection} {Received Signal}
		In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation} \label{eq:y_{m,k}(t)}
			y_{m,k}(t)=\Re\left\{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}}\right\}
		\end{equation}
		Therefore, the RF input signal to the antenna of user $k$ writes as
		% \begin{equation}

		% \end{equation}
		% \begin{equation} \label{eq:y_{m,k}(t)}
		% 	\begin{split}
		% 		y_{m,k}(t)
		% 		&= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\} \\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\} \\
		% 		&\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
		% 		&= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\} \\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}
		% 	\end{split}
		% \end{equation}
		% Therefore, the RF signal input to the antenna at user $k$ is
		% \begin{equation} \label{eq:y_{k}(t)}
		% 	y_{k}(t) = \sum_{m=1}^{M} y_{m,k}(t)
		% \end{equation}
	\end{subsection}
\end{section}
